Vagueness, Noise, and Signaling

### 2015-01-27 paper/version_02/paper.tex
Revision 1, final sent

As a result, dynamics on behavioral strategies are more coarse-grained
and not necessarily equivalent to dynamics on mixed strategies. An
advantage of dynamics in behavioral strategies is that they reduce
complexity, which helps with numerical simulations. They might also be
a more natural choice for cultural dynamics, e.g., when an agent
observes and imitates another agent's strategy: it may be more
plausible that agents adopt the use of a single word, not an entire
lexicon, so to speak. On the other hand, biological evolution seems
more naturally modeled in terms of mixed strategies, since it is a full
set of behavioral disposition that is bequeathed to the next
generation.

@@

Admittedly, this argument hinges on the choice of utility
function. Still, to the extent that the utility functions we chose are
reasonable---and we think they are very reasonable---the case
suggests that quantal responses alone are not a good model for why
linguistic categories are vague. With respect to this issue, perceptual
confusion of similar states produces more intuitive predictions. What
is more plausible, though, is that both perceptual confusion \emph{and}
computational errors in maximizing expected utility play a role in
making vague categorization a pervasive feature of natural language
meaning. Perhaps even further factors, such as limited observations,
imperfect memory, and more, should be considered in order to form
a more complete understanding of the phenomenon of vagueness.

>>>>

As a result, dynamics on behavioral strategies are more coarse-grained
and not necessarily equivalent to dynamics on mixed strategies. An
advantage of dynamics in behavioral strategies is that they reduce
complexity, which helps with numerical simulations. They might also be
a more natural choice for cultural dynamics, e.g., when an agent
observes and imitates another agent's strategy: it may be more
plausible that agents adopt the use of a single word, not an entire
lexicon, so to speak. On the other hand, biological evolution seems
more naturally modeled in terms of mixed strategies whenever it is a
full set of behavioral disposition that is bequeathed to the next
generation.

@@

Admittedly, this argument hinges on the choice of utility
function. Still, to the extent that the utility functions we chose are
reasonable---and we think they are very reasonable---the case suggests
that quantal responses alone are not a good model for why linguistic
categories are vague. With respect to this issue, perceptual confusion
of similar states produces more intuitive predictions. What is more
plausible, though, is that both perceptual confusion \emph{and}
computational errors in maximizing expected utility play a role in
making vague categorization a pervasive feature of natural language
meaning. Perhaps even further factors, such as limited observations,
imperfect memory or uncertainty about the exact prior distribution of
states, should be considered in order to form a more complete
understanding of the phenomenon of vagueness.
